A standardized framework for risk-based assessment of treatment effect heterogeneity in observational healthcare databases

### 2021-09-12 submission/manuscript.rmd
include resutls from all databases; closes #1
first draft of response

The aim of this step is the estimation of treatment effects (both on the
relative and the absolute scale) within risk strata---typically 4 risk
quarters---defined using the prediction model of step 3. Any appropriate method
for the evaluation of relative and absolute treatment effects can be considered,
as long as the this is done consistently in all risk strata. Common approaches
are odds ratios or hazard ratios for relative scale estimates and differences in
observed proportions or differences in Kaplan-Meier estimates for absolute scale
estimates, depending on the problem at hand. We estimate propensity scores
within risk strata which we then use to match patients from different treatment
cohorts or stratify them into groups with similar propensity scores or to weigh
each patient's contribution to the estimation process [@Austin2011].

@@

@@

```{r covariateBalance, cache = TRUE, echo=FALSE, fig.cap="Patient charactersistic balance for ACE inhibitors and beta blockers before and after stratification on the propensity scores. Each dot represents the standardized difference of means for a single covariate before (x-axis) and after (y-axis) stratification", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/CovariateBalance.tiff")))
```

>>>>

The aim of this step is the estimation of treatment effects (both on the
relative and the absolute scale) within risk strata---typically 4 risk
quarters---defined using the prediction model of step 3.

***Effect estimation may be focused on the difference in outcomes for a randomly
selected person from the risk stratum (average treatment effect) or for a
randomly selected person from the treatment cohort within the risk stratum
receiving the treatment under study (average treatment effect on the
treated).***

Any appropriate method for the evaluation of relative and absolute treatment
effects can be considered, as long as the this is done consistently in all risk
strata. Common approaches are odds ratios or hazard ratios for relative scale
estimates and differences in observed proportions or differences in Kaplan-Meier
estimates for absolute scale estimates, depending on the problem at hand. We
estimate propensity scores within risk strata which we then use to match
patients from different treatment cohorts or stratify them into groups with
similar propensity scores or to weigh each patient's contribution to the
estimation process [@Austin2011].

@@

***Our aim was to estimate the average treatment effects on the relative and the
absolute scale within strata of predicted acute MI risk.***

@@

```{r covariateBalance, cache = TRUE, echo=FALSE, fig.cap="Patient characteristic balance for ACE inhibitors and beta blockers before and after stratification on the propensity scores. Each dot represents the standardized difference of means for a single covariate before (x-axis) and after (y-axis) stratification", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/CovariateBalance.tiff")))
```
